### 2020-01-25 experiments.tex
Add confirmation stuff

\subsubsection{Confirmation of Results}  Because our random contracts' quality might be low, we also checked our results on 30 contracts from the Solidity documentation, the \emph{Mastering Ethereum} book \cite{masteringEth}, and a handful of selected, recent, higher quality blockchain contracts.  Slither had a mean mutation score of 0.11, vs. 0.4 for SmartCheck and 0.01 for Securify.  Associated mutant ratios were 0.38, 0.08, and close to zero.  Mutant kill overlap was also similar (in fact, Figure \ref{fig:examplevenn} shows the results; Slither is A, SmartCheck is B, and Securify is C.

>>>>

\subsubsection{Confirmation of Results}  Because our random contracts' quality might be low, we also checked our results on 30 contracts from the Solidity documentation, the \emph{Mastering Ethereum} book \cite{masteringEth}, and a handful of selected, recent, higher quality blockchain contracts.  Slither had a mean mutation score of 0.11, vs. 0.4 for SmartCheck, and 0.01 for Securify.  Associated mutant ratios were 0.38, 0.08, and $<$ 0.0001.  Mutant kill overlap was also similar; in fact, Figure \ref{fig:examplevenn} shows the results: Slither is A, SmartCheck is B, and Securify is C.
